full title

### 2020-09-01 paper/pldi21/abstract.tex
Updated the title and abstract.

\begin{abstract}
Static analyses based on abstract interpretation can be integrated into developer workflow and help developers to find bugs.
However, the dynamic features of JavaScript degrade the scalability and precision of the pure static bug detection.
Combining static and dynamic analyses is one of the breakthroughs in JavaScript bug detection.
Existing combined analyses have clear boundaries that apply which analysis to which part.
Such boundaries are intuitive but limit chances to optimize transitions between two analyses.
We formally present dynamic shortcuts, a more flexible compound of static and dynamic analyses.
We implement a proof of concept bug detector by extending the existing JavaScript static analyzer for a subset of ECMAScript 5.1.
Our experimental results show that adding dynamic shortcuts indeed speeds up the detection and provides more precise bug reports.
\end{abstract}

>>>>

\begin{abstract}
Static analyses based on abstract interpretation can be integrated into developer workflow and help developers to find bugs.
However, the dynamic features of JavaScript degrade the scalability and precision of the pure static analyses.
Combining static and dynamic analyses is one of the breakthroughs in JavaScript bug detection.
Existing combined analyses have static boundaries that distinguish which analysis used for which part of a program.
Such boundaries are intuitive but limit chances to optimize transitions between two analyses.
We formally present dynamic shortcuts, a more flexible compound of static and dynamic analyses.
We implement a proof of concept bug detector by extending the existing static analyzer supporting a subset of ECMAScript 5.1.
Our experimental results show that adding dynamic shortcuts indeed speeds up the detection and provides more precise bug reports.
\end{abstract}
